Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Clarify why we care about wake recovery

To get an overall idea of the wake recovery predicted by each model, we
rearrange the streamwise component of the Navier--Stokes equation to isolate
$\partial U / \partial x$---following Bachant and
Wosnik~\cite{Bachant2015-JoT}---and compute each term at $X/D = 1$ to compare
with the experimental results.

>>>>

To get an overall idea of the wake recovery predicted by each model, and
therefore its potential effectivness in evaluating array spacing, the streamwise
component of the Navier--Stokes equation was rearranged to isolate $\partial U /
\partial x$---following Bachant and Wosnik~\cite{Bachant2015-JoT}---and compute
each term at $X/D = 1$ to compare with the experimental results.
